Gametic Selection, Sex Ratio Bias, and Transitions Between Sex Determination Systems

### 2016-09-26 LaTeX/Turnover.tex
comparison to Kirk complete

For the neo-$Y$ we have $C_Y = (r - R)s^f $.
The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t^m\neq0$).
This differs from \cite{vanDoorn:2007eu}

For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$.
In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade.
For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).

>>>>

For the neo-$Y$ we have $C_Y = (r - R)s^f $.
The neo-$Y$ can therefore invade whenever it is in tighter linkage with the selected locus than the ancestral sex-determining locus, $r>R$, provided locus \textbf{A} is polymorphic ($V_A>0$) and there is selection among both females ($s^f\neq0$) and gametes/gametophytes from males ($t^m\neq0$).
This reduces to the weak linkage results of \cite{vanDoorn:2007eu} when we do not assume equal dominance coefficients in the two sexes, there is no haploid selection, and there is free recombination between locus \textbf{A} and one of the sex-determining regions.

For the neo-$W$ we have $C_W = [(2r(1-R)-R) s^f + (1-2r)R s^m]/2$.
In this case, even when the novel sex-determining locus is in looser linkage with the selected locus than the ancestral sex-determining locus is, $r<R$, a neo-$W$ can invade.
For example, with $R=1/2$ the neo-$W$ invades if there is any linkage between the ancestral sex-determining and selected loci ($r<1/2$), there is selection among gametes/gametophytes in males ($t^m\neq0$), and there is selection for or against $A$ in both males and females ($s^m s^f >0$) that is stronger in males than in females ($|s^m| > |s^f|$).
This reduces to the weak linkage results of \cite[][Equation 3]{vanDoorn:2010hu} when we do not assume equal dominance coefficients in the two sexes and there is no haploid selection.
